Quantifying the manageability of pollination networks in an invasion context

### 2017-06-16 paper/manuscript.Rmd
Add brief description of cycles in the methids

Given the respective dependences, the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
This simplification, while maintaining ecological realism, is advantageous for several reasons. 
First, it is consistent with previous advances in structural controllability; second, it avoids complications related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
Moreover, we found that changing to unidirectional interactions based on the direction of asymmetry does not alter the relative *n~D~* of different networks (Table S3).

>>>>

Given the respective dependences, the extent to which species *i* affects species *j* relative to the extent to which *j* affects *i* can be summarised by the interaction asymmetry [@Bascompte2006] given by $$a(i,j) = a(j,i) = \frac{\left | d_{ij}-d_{ji} \right |}{max\left ( d_{ij}, d_{ji} \right )}.$$
Previous research has shown that mutual dependences are often highly asymmetric in natural communities [@Bascompte2006]; in other words, if a plant species is largely dependent on a pollinator species, then that pollinator tends to depend rather weakly on the plant (or vice versa). 
We therefore simplified the network so that interacting species are connected by only one directed link when mutual dependences are asymmetric (Figure 2c).
This simplification, while maintaining ecological realism, is advantageous for several reasons. 
First, it is consistent with previous advances in structural controllability; second, it prevents the singular case in which the network could be perfectly matched rendering $D=1$ as well as problems related to the introduction of artificial control cycles [@Ruths2014]; and third it significantly reduces the computational resources necessary for the application of our approach (Supporting Information S6).
Moreover, we found that changing to unidirectional interactions based on the direction of asymmetry does not alter the relative *n~D~* of different networks (Table S3).
